Beam-Helicity and Beam-Charge Asymmetries \\ in the Bethe-Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS0607 (v1.2)} \underline{Drafting Committee: DC90 (\today)}

### 2011-07-26 background_and_systematic_dual.tex
Update text

\red{A} contribution to the systematic uncertainties of the
  measured amplitudes \red{arises} from shift\red{s in}  the
missing-mass distributions\red{. Such shifts appear in a comparison of} electron and positron data~\cite{Zei09,Bur10}. The missing-mass distribution is also adjusted for each calorimeter calibration period of data
collected in 2007 to account for an observed time dependence. One
quarter of the difference between the asymmetries extracted using the standard
and shifted missing-mass windows is taken as the corresponding systematic
uncertainty.

The predominant contributio to the systematic uncertainty arises from detector
effects, including the acceptance of the spectrometer, smearing
effects due to detector resolution and radiative processes during
  detection, (e.g. of the photon in the calorimeter \cite{Bur10}), and
the finite bin width of the $-t$, $x_{\textrm{B}}$ and $Q^{2}$ projections. In order to quantify these effects, events were generated using a Monte Carlo simulation of the spectrometer that included them. An event
generator based on the GPD model described in ref.~\cite{Van99,Goe01} was
used for the simulation because it describes the data well and \red{was employed in r}ef.~\cite{Air09}. Asymmetry amplitudes were extracted
from these simulated events using the same analysis procedure used to
extract amplitudes from experimental data. In each kinematic bin, the
systematic uncertainty was determined as the difference between the asymmetry amplitude reconstructed from the simulated data and that
\red{calculated} from the GPD model at the average $-t$, $x_{\textrm{B}}$ and
$Q^{2}$ value for that bin.

>>>>

\red{A} contribution to the systematic uncertainties of the
  measured amplitudes \red{arises} from shift\red{s in}  the
missing-mass distributions\red{. Such shifts appear in a comparison of} electron and positron data~\cite{Zei09,Bur10}. One
quarter of the difference between the asymmetries extracted using the standard
and shifted missing-mass windows is taken as the corresponding systematic
uncertainty.

The predominant contributio to the systematic uncertainty arises from detector
effects, including the acceptance of the spectrometer, smearing
effects due to detector resolution and radiative processes during
  detection, and
the finite bin width of the $-t$, $x_{\textrm{B}}$ and $Q^{2}$ projections. In order to quantify these effects, events were generated using a Monte Carlo simulation of the spectrometer that included them. An event
generator based on the GPD model described in ref.~\cite{Van99,Goe01} was
used for the simulation because it describes the data well and \red{was employed in r}ef.~\cite{Air09}. Asymmetry amplitudes were extracted
from these simulated events using the same analysis procedure used to
extract amplitudes from experimental data. In each kinematic bin, the
systematic uncertainty was determined as the difference between the asymmetry amplitude reconstructed from the simulated data and that
\red{calculated} from the GPD model at the average $-t$, $x_{\textrm{B}}$ and
$Q^{2}$ value for that bin.

### 2011-07-26 experiment_and_data.tex
Update text

An event sample was selected using a missing-mass technique requiring
that the squared missing-mass $M_{\textrm{X}}^{2}=(q+P-q')^{2}$
of the $e\,p \rightarrow\, e'\,\gamma\, \textrm{X}$ measurement
corresponded to the square of the proton mass within the limits of the
energy resolution of the H{\sc ermes} calorimeter. Here, $q$ is the four-momentum of the virtual photon, $p$ is the initial four-momentum of the target proton and $q'$ is the four-momentum of the produced photon. The ``exclusive region'' was defined as $-$($1.5$\,GeV)$^{2} < M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in ref.~\cite{Air09}. This exclusive region was shifted by up to 0.17\,GeV$^{2}$ to reflect observed differences in the distributions of the electron and positron data samples and to account for the time dependence of the missing-mass distributions observed in the 2007 data set \cite{Bur10}.

@@

The $A^{\cos(3\phi)}_{\textrm{C}}$ amplitude depends on the
$c_{3,\textrm{unp}}^{\textrm{I}}$ Fourier coefficient and hence the
$\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ function. Although the CFFs
in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$,
where $\alpha_{\textrm{S}}$ is the strong coupling constant.
\begin{table}
\begin{center}
\resizebox{\textwidth}{!} {
\begin{tabular}{|c|c|c|c|c|}
\hline
Asymmetry Amplitude& Fourier Coefficient& Dominant CFF Dependence & Twist Level & Relative Suppression   \\ 
\hline
\hline
$A_{\textrm{LU,I}}^{\sin\phi}$ & $s_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  2 & --\\
\hline
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ & $s_{2,\textrm{unp}}^{\textrm{I}}$ 
&
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  3 & $1/Q$\\
\hline
\hline
$A_{\textrm{LU,DVCS}}^{\sin\phi}$ & $s_{1, \textrm{unp}}^{\textrm{DVCS}}$ &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ &  3 & $1/Q$ \\
\hline
\hline
$A_{\textrm{C}}^{\cos(0\phi)}$ & $c_{0,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2&kinematic
\\
\hline
$A_{\textrm{C}}^{\cos\phi}$ & $c_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2 & --
\\
\hline
$A_{\textrm{C}}^{\cos(2\phi)}$ & $c_{2,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 3 & $1/Q$ \\
\hline
$A_{\textrm{C}}^{\cos(3\phi)}$ & $c_{3,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ &  2 & $\alpha_{\textrm{S}}/\pi$ \\
\hline
 \end{tabular}
}
\caption{Asymmetry amplitudes that can
be extracted from the available data set, the related Fourier coefficients,
 the $\mathcal{C}$-functions, the twist level and the suppression
 relative to the leading amplitudes at H{\sc ermes} kinematic conditions~\cite{Bel02b}.}
\label{tab_amplitudes}
\end{center}
\end{table}

>>>>

An event sample was selected using a missing-mass technique requiring
that the squared missing-mass $M_{\textrm{X}}^{2}=(q+P-q')^{2}$
of the $e\,p \rightarrow\, e'\,\gamma\, \textrm{X}$ measurement
corresponded to the square of the proton mass within the limits of the
energy resolution of the H{\sc ermes} calorimeter. Here, $q$ is the four-momentum of the virtual photon, $p$ is the initial four-momentum of the target proton and $q'$ is the four-momentum of the produced photon. The ``exclusive region'' was defined as $-$($1.5$\,GeV)$^{2} < M_{\textrm{X}}^{2}$ $<$ (1.7\,GeV)$^{2}$, as in ref.~\cite{Air09}. This exclusive region was shifted by up to 0.17\,GeV$^{2}$ to reflect observed differences in the distributions of the electron and positron data samples~\cite{Bur10}.

@@

The $A^{\cos(3\phi)}_{\textrm{C}}$ amplitude depends on the
$c_{3,\textrm{unp}}^{\textrm{I}}$ Fourier coefficient and hence the
$\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ function. Although the CFFs
in this function are of leading twist, they relate to gluon helicity-flip GPDs and are thus suppressed by $\alpha_{\textrm{S}}/\pi$,
where $\alpha_{\textrm{S}}$ is the strong coupling constant.
\begin{table}
\begin{center}
\resizebox{\textwidth}{!} {
\begin{tabular}{|c|c|c|c|c|}
\hline
Asymmetry Amplitude& Fourier Coefficient& Dominant CFF Dependence & Twist Level & Relative Suppression   \\ 
\hline
\hline
$A_{\textrm{LU,I}}^{\sin\phi}$ & $s_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  2 & --\\
\hline
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ & $s_{2,\textrm{unp}}^{\textrm{I}}$ 
&
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$
&  3 & $1/Q$\\
\hline
\hline
$A_{\textrm{LU,DVCS}}^{\sin\phi}$ & $s_{1, \textrm{unp}}^{\textrm{DVCS}}$ &
$\mathfrak{Im}\mathcal{C}_{\textrm{unp}}^{\textrm{DVCS}}$ &  3 & $1/Q$ \\
\hline
\hline
$A_{\textrm{C}}^{\cos(0\phi)}$ & $c_{0,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2& $\frac{(2-y)^2K}{(1-y)(2-2y+y^2)}$
\\
\hline
$A_{\textrm{C}}^{\cos\phi}$ & $c_{1,\textrm{unp}}^{\textrm{I}}$  &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 2 & --
\\
\hline
$A_{\textrm{C}}^{\cos(2\phi)}$ & $c_{2,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{unp}}^{\textrm{I}}$ & 3 & $1/Q$ \\
\hline
$A_{\textrm{C}}^{\cos(3\phi)}$ & $c_{3,\textrm{unp}}^{\textrm{I}}$ &
$\mathfrak{Re}\mathcal{C}_{\textrm{T,unp}}^{\textrm{I}}$ &  2 & $\alpha_{\textrm{S}}/\pi$ \\
\hline
 \end{tabular}
}
\caption{Asymmetry amplitudes that can
be extracted from the available data set, the related Fourier coefficients,
 the $\mathcal{C}$-functions, the twist level and the suppression
 relative to the leading amplitudes at H{\sc ermes} kinematic conditions. {The constant K is defined in ref.~\cite{Bel02b}}.}
\label{tab_amplitudes}
\end{center}
\end{table}

### 2011-07-26 results_dual.tex
Update text

\section{Results}
Results for the beam-helicity and beam-charge asymmetry amplitudes extracted separately from previously published 1996-2005 and the new 2006-2007 hydrogen data sets, are presented in Figs.~\ref{release_bsa_0607} and~\ref{release_bca_0607}. Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$. All of the extracted asymmetry amplitudes are subject to a fractional contribution to the event yield from associated production (``Assoc. fraction''), which is shown in the bottom row of each figure. The beam-helicity asymmetry amplitudes are subject to an additional scale uncertainty from the measurement of the beam polarisation, which is stated in the captions of the figures.
\begin{figure}
\begin{center}
\includegraphics[width=15cm,keepaspectratio]{bsadvcsplots_eml_par13_bin6_pic_0607_9605_cluster_dual}
  \caption{Beam-helicity asymmetry amplitudes extracted separately from
the 1996-2005 (open triangles) and 2006-2007 (filled squares)
hydrogen data. The inner error bars represent the statistical uncertainties, while total error bars denote the statistical and systematic uncertainties added in quadrature.  
An additional 2.8\,\% and 3.4\,\% scale uncertainty for the 1996-2005 and
2006-2007 data respectively is present in the amplitudes due to the \red{imprecision} of
the beam polarisation measurement. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
 \label{release_bsa_0607}
\end{center}
 \end{figure}

@@

The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are
sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of Fig.~\ref{bsa_xbjrange}. The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest magnitude of any of the amplitudes when extracted in a single bin from the entire data set. This amplitude shows no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must approach zero as $-t$ approaches zero due to the dependence of the amplitude on the factor $k$ from Eq.~\ref{eq:s1}. The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$. The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ asymmetry is shown in the second row of Fig.~\ref{bsa_xbjrange}. Both the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitude and the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ asymmetry are compatible with zero, and neither asymmetry shows any dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$. The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations that reflect the equipment used in the various stages of the H{\sc ermes} experiment. Monte Carlo events propogated through simulations of the two experimental \red{arrangements} are mixed in proportion to the data yield observed for the two data periods and the relevant studies on background processes and detector effects in Sec. 4 were completed. The missing-mass uncertainty for the combined data set is calculated similarly to the procedure described in that section and the results added in quadrature.

The $A_{\textrm{C}}^{\cos(n\phi)}$ amplitudes are shown in Fig.~\ref{bca_xbjrange}. The systematic uncertainties are estimated in a similar procedure as for those for the beam-helicity asymmetries. The leading-twist $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ amplitudes are both non-zero. There is a\red{n expected} relationship between $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ as the Fourier coefficient $c^{\textrm{I}}_{0,\textrm{unp}}$ is inversely proportional to $c^{\textrm{I}}_{1,\textrm{unp}}$ via the kinematic factor $k$ from Eq.~\ref{eq:c1}. These amplitudes \red{are found to} diverge with opposite sign from zero at increasing values of $-t$ but they
have no discernible dependence on $x_{\textrm{B}}$ and $Q^{2}$. The $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ amplitudes are both consistent with zero and have no significant variation in value over the range in $-t$, $x_{\textrm{B}}$ and $Q^{2}$. The $A_{C}^{\cos(2\phi)}$ amplitude is related to twist-3 GPDs and $A_{\textrm{C}}^{\cos(3\phi)}$ relates to gluon helicity-flip GPDs. Both of these amplitudes are expected to be suppressed at H{\sc ermes} kinematic conditions compared to the leading-twist amplitudes.

The curves in  Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the results of model calculations at the centere of the kinematic bins used for the data extractions. The solid and dashed curves show calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from H{\sc ermes} and Jefferson Laboratory, and the collider experiments at H{\sc era}. The basic model is a minimalist dual representation of GPDs with only (very) weakly entangled skewness and $t$ dependences. In this model, the $t$ dependence is approximated by a physically motivated Regge dependence. The solid curves represent the model fit without data from experiments \cite{Cam06, Gir08} at Hall A of Jefferson Laboratory; the model fit represented by the dashed curves includes these data. Both fits include the 1996-2005 H{\sc ermes} data. The model incorporates only twist-2 GPDs and so can provide results only for the $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes. All of the \red{relevant} amplitudes \red{reported here} are well described by the model.

>>>>

\section{Results}
Results for the beam-helicity and beam-charge asymmetry amplitudes extracted separately from previously published 1996-2005 and the new 2006-2007 hydrogen data sets are presented in Figs.~\ref{release_bsa_0607} and~\ref{release_bca_0607}. Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$. All of the extracted asymmetry amplitudes are subject to a fractional contribution to the event yield from associated production (``Assoc. fraction''), which is shown in the bottom row of each figure. The beam-helicity asymmetry amplitudes are subject to an additional scale uncertainty from the measurement of the beam polarisation, which is stated in the captions of the figures.
\begin{figure}
\begin{center}
\includegraphics[width=15cm,keepaspectratio]{bsadvcsplots_eml_par13_bin6_pic_0607_9605_cluster_dual}
  \caption{Beam-helicity asymmetry amplitudes extracted separately from
the 1996-2005 (open triangles) and 2006-2007 (filled squares)
hydrogen data. The inner error bars represent the statistical uncertainties, while total error bars denote the statistical and systematic uncertainties added in quadrature.  
An additional 2.8\,\% and 3.4\,\% scale uncertainty for the 1996-2005 and
2006-2007 data respectively is present in the amplitudes due to the \red{imprecision} of
the beam polarisation measurement. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
 \label{release_bsa_0607}
\end{center}
 \end{figure}

@@

The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are
sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of Fig.~\ref{bsa_xbjrange}. The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest magnitude of any of the amplitudes when extracted in a single bin from the entire data set. This amplitude shows no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must approach zero as $-t$ approaches zero due to the dependence of the amplitude on the factor $k$ from Eq.~\ref{eq:s1}. The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$. The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ asymmetry is shown in the second row of Fig.~\ref{bsa_xbjrange}. Both the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ \red{asymmetry} amplitude and the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ asymmetry \red{amplitude} are compatible with zero, and neither asymmetry \red{amplitude} shows any dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$. The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations \red{as explained in section~4}. The missing-mass uncertainty for the combined data set \red{was} calculated \red{using} the procedure described in that section and the results \red{were} added in quadrature.

The $A_{\textrm{C}}^{\cos(n\phi)}$ amplitudes are shown in Fig.~\ref{bca_xbjrange}. The systematic uncertainties are estimated in \red{the same} procedure as for those for the beam-helicity asymmetries. The leading-twist $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ amplitudes are both non-zero. There is a\red{n expected} relationship between $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ as the Fourier coefficient $c^{\textrm{I}}_{0,\textrm{unp}}$ is inversely proportional to $c^{\textrm{I}}_{1,\textrm{unp}}$ via the kinematic factor $k$ from Eq.~\ref{eq:c1}. These amplitudes \red{are found to} diverge with opposite sign from zero at increasing values of $-t$ but they
have no discernible dependence on $x_{\textrm{B}}$ and $Q^{2}$. The $A_{\textrm{C}}^{\cos(2\phi)}$ and $A_{\textrm{C}}^{\cos(3\phi)}$ amplitudes are both consistent with zero and have no significant variation in value over the range in $-t$, $x_{\textrm{B}}$ and $Q^{2}$. The $A_{C}^{\cos(2\phi)}$ amplitude is related to twist-3 GPDs and $A_{\textrm{C}}^{\cos(3\phi)}$ relates to gluon helicity-flip GPDs. Both of these amplitudes are expected to be suppressed at H{\sc ermes} kinematic conditions compared to the leading-twist amplitudes.

The curves in  Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the results of model calculations at the \red{average value} of the kinematic bins used for the data extractions. The solid and dashed curves show calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from H{\sc ermes} and Jefferson Laboratory, and the collider experiments at H{\sc era}. The basic model is a minimalist dual representation of GPDs with only (very) weakly entangled skewness and $t$ dependences. In this model, the $t$ dependence is approximated by a physically motivated Regge dependence. The solid curves represent the model fit without data from experiments \cite{Cam06, Gir08} at Hall A of Jefferson Laboratory; the model fit represented by the dashed curves includes these data. Both fits include the 1996-2005 H{\sc ermes} data. The model incorporates only twist-2 GPDs and so can provide results only for the $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes. All of the \red{relevant} amplitudes \red{reported here} are well described by the model.

### 2011-07-26 theory.tex
Update text

\section{Introduction}
Generalised Parton Distributions (GPDs)
\cite{Mue94,Ji97a,Rad97} encompass the familiar parton
distribution functions (PDFs) and nucleon form factors to provide a
comprehensive description of the structure of the nucleon.
Although GPDs are difficult to access experimentally, the H{\sc ermes}
collaboration has previously published results
\cite{Air01,Air06,Air08,Air09,Air10, Air10a, Air10b, Air11} on
the leptoproduction of real photons from a nucleon or nucleus that can
be used to constrain GPDs via Compton Form Factors (CFFs). A thorough
desccription of the nucleon in terms of GPDs would allow the deduction
of the total angular momentum of partons in the nucleon\red{,} and the
construction of a longitudinal-momentum\red{-}dissected transverse spatial map of parton positions.

@@

\begin{figure}
\begin{center}
\subfigure[DVCS]{\includegraphics[width=5.6cm]{dvcs}}
\hspace{3cm}
\subfigure[Bethe Heitler]{\includegraphics[width=5.2cm]{1_bh}}
\caption[DVCS and Bethe Heitler hand bag diagram.]{(a): The DVCS process in
which an electron/positron ($e$) interacts with a quark in the nucleon
($p$) via a virtual photon ($\gamma^\ast$). The quark is found in the
nucleon with longitudinal momentum fraction $x+\xi$ and emits a real
photon ($\gamma$). The quark is absorbed by the nucleon with
longitudinal momentum fraction
$x-\xi$. (b): The Bethe-Hietler process, i.e. the emission of a real photon from the scattering or
scattered lepton. It has the same initial and final states as DVCS.}
\label{spin}
\end{center}
\end{figure}

>>>>

\section{Introduction}
Generalised Parton Distributions (GPDs)
\cite{Mue94,Ji97a,Rad97} encompass the familiar parton
distribution functions (PDFs) and nucleon form factors to provide a
comprehensive description of the structure of the nucleon.
Although GPDs are difficult to access experimentally, the H{\sc ermes}
collaboration has previously published results
\cite{Air01,Air06,Air08,Air09,Air10, Air10a, Air10b, Air11} on
the leptoproduction of real photons from a nucleon or nucleus that can
be used to constrain GPDs via Compton Form Factors (CFFs). A thorough
description of the nucleon in terms of GPDs would allow the deduction
of the total angular momentum of partons in the nucleon\red{,} and the
construction of a longitudinal-momentum\red{-}dissected transverse spatial map of parton positions.

@@

\begin{figure}
\begin{center}
\subfigure[DVCS]{\includegraphics[width=5.6cm]{dvcs}}
\hspace{3cm}
\subfigure[Bethe Heitler]{\includegraphics[width=5.2cm]{1_bh}}
\caption[DVCS and Bethe Heitler hand bag diagram.]{(a): The DVCS process in
which an electron/positron ($e$) interacts with a quark in the nucleon
($p$) via a virtual photon ($\gamma^\ast$). The quark is found in the
nucleon with longitudinal momentum fraction $x+\xi$ and emits a real
photon ($\gamma$). The quark is absorbed by the nucleon with
longitudinal momentum fraction
$x-\xi$. (b): The Bethe-H\red{ei}tler process, i.e. the emission of a real photon from the scattering or
scattered lepton. It has the same initial and final states as DVCS.}
\label{spin}
\end{center}
\end{figure}
